\documentclass[10pt,a4paper]{article}

% -------------------- Packages --------------------
\usepackage[left=0.9in,right=0.9in,top=0.8in,bottom=0.8in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fontawesome5}

% -------------------- Formatting --------------------
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}

\titleformat{\section}
  {\bfseries}
  {}
  {0pt}
  {}
  [\color{blue}\rule{\linewidth}{0.5pt}]

\titlespacing*{\section}{0pt}{8pt}{5pt}

\begin{document}

% -------------------- Header --------------------
\begin{center}
    {\Large \textbf{Manotosh Maity}} \\[4pt]
    \faEnvelope\ \href{mailto:manotoshmaity7@gmail.com}{manotoshmaity7@gmail.com}
    \quad —
    \quad \faPhone\ +91-9907300447
    \quad —
    \quad \faGithub\ \href{https://github.com/manotoshmaity} manotosh
    \quad —
    \quad \faLinkedin\ \href{https://www.linkedin.com/in/manotosh-maity} LinkedIn
\end{center}

% -------------------- Career Objective --------------------
\section*{Career Objective}
Motivated Computer Science undergraduate specializing in Artificial Intelligence and Machine Learning, with strong skills in full-stack development and data-driven problem solving. Seeking an opportunity to apply my knowledge of machine learning, NLP, and modern web technologies to build scalable real-world applications while continuously learning and contributing to organizational growth.

% -------------------- Education --------------------
\section*{Education}
\textbf{Brainware University} \hfill \textbf{CGPA: 8.82 — 83.7\%} \\
B.Tech in Computer Science and Engineering (AI \& ML)

% -------------------- Skills --------------------
\section*{Skills}
\textbf{Languages:} C, Python, Java, HTML, CSS, JavaScript, PHP \\
\textbf{Frameworks \& Libraries:} Next.js, React.js, Node.js, FastAPI, Django \\
\textbf{Data Science \& ML:} Pandas, Scikit-learn, Matplotlib, Deep Learning, NLP \\
\textbf{Databases:} MongoDB, SQL \\
\textbf{Tools:} Figma, NPM \\
\textbf{Domain Expertise:} Machine Learning, Full Stack Development

% -------------------- Projects --------------------
\section*{Projects}

\textbf{VLM} \hfill \href{https://huggingface.co/spaces/pal2004/Vlm-search} Live
\begin{itemize}[noitemsep]
    \item Designed and implemented a visual search engine leveraging Vision-Language Models (VLMs).
    \item Developed a shared embedding space for effective text–image retrieval.
    \item Managed database systems for efficient multimodal embedding storage and indexing.
\end{itemize}

\textbf{MindCare} \hfill \href{https://mindcarees.netlify.app/} Live
\begin{itemize}[noitemsep]
    \item Developed an AI-powered platform for mental health assessment and counseling.
    \item Integrated emotional analytics, self-assessment tools, and real-time counseling.
    \item Built interactive dashboards using Recharts with responsive UI.
\end{itemize}

\textbf{Zentro} \hfill \href{https://zentro-jn9u.onrender.com/} Live
\begin{itemize}[noitemsep]
    \item Built a responsive MERN stack eCommerce platform with authentication and cart features.
\end{itemize}

% -------------------- Training --------------------
\section*{Virtual Experience Programs \& Technical Training}
\begin{itemize}[noitemsep]
    \item \textbf{Euphoria GenX (SEP 2025):} Designed scalable MERN applications.
    \item \textbf{IBM Cloud (AUG 2025):} Hands-on experience with IaaS, PaaS, SaaS.
    \item \textbf{Spoken Tutorial (Jul 2024):} Java programming via IIT Bombay.
    \item \textbf{Intel Unnati (Apr 2025):} Deep Learning, Machine Learning, NLP.
    \item \textbf{NIELIT (Jun 2025):} Blockchain, Big Data, Data Science (FutureSkills PRIME).
\end{itemize}

% -------------------- Achievements --------------------
\section*{Achievement and Extra Curricular Activities}
\begin{itemize}[noitemsep]
    \item Solved 100+ DSA problems on LeetCode
    \item Joined R-programming workshop
\end{itemize}

\end{document}
